VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_intro.tex
a

Commercial ``Infrastructure as a Service'' clouds (i.e. {\em public
clouds}) often make use of commodity data center components to achieve the
best possible economies of scale.  In particular, large-scale e-commerce cloud
providers such as Google and Alibaba deploy ``converged'' components that
co-locate computing and storage in each hardware module (as opposed to having
separate computing and storage ``tiers.'')  The advantage of such an approach
is that all infrastructure components are used to support paying customers --
there are no resources specifically dedicated to cloud services.
%One of emerging architectures for building cloud services is a converged
%storage architecture that leverages commodity servers with software clustered
%storage.
%The converged architecture (server plus compute in same tier) grew out of the
%Google model. 
In particular, these providers use software to
aggregate multiple direct attached low-cost disks together across
servers as a way of avoiding the relatively high cost of network attached 
storage~\cite{googlefs03,hdfs10}.
%systems. %This(e.g. ~\cite{NutanixPaper}).  Leading cloud platform companies
%such as Google, Amazon, Alibaba, Microsoft Azure  have built a converged
%compute and storage infrastructure and used a distributed file system such as
%Google file system~\cite{googlefs03,hdfs10} to glue a large number of
%commodity servers.
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the
%costs and performance limitations associated with network storage.
each physical machine runs a number of virtual machines (VMs)
%as  instances of a guest operating system 
and their virtual disks are stored as disk image files.
% typically using a local (possibly shared) file system.
Frequent snapshot backup of virtual machine images can
increase the service reliability by allowing VMs to restart from their latest
snapshot in the event of a server failure. Snapshots contain highly redundant content chunks and 
%  However, because the disk
%blocks that make up the VMs are often the same from snapshot to snapshot
%and are shared among VMs,  
deduplication of redundant 
content~\cite{venti02,bottleneck08} is necessary to substantially reduce the
storage demand.

>>>>

Commercial ``Infrastructure as a Service'' clouds (i.e. {\em public
clouds}) often make use of commodity data center components to achieve the
best possible economies of scale.  In particular, large-scale e-commerce cloud
providers such as Google and Alibaba deploy ``converged'' components that
co-locate computing and storage in each hardware module (as opposed to having
separate computing and storage ``tiers.'')  The advantage of such an approach
is that all infrastructure components are used to support paying customers --
there are no resources specifically dedicated to cloud services~\cite{NutanixPaper}.
%One of emerging architectures for building cloud services is a converged
%storage architecture that leverages commodity servers with software clustered
%storage.
%The converged architecture (server plus compute in same tier) grew out of the
%Google model. 
In particular, these providers use software to
aggregate multiple direct attached low-cost disks together across
servers as a way of avoiding the relatively high cost of network attached 
storage~\cite{googlefs03,hdfs10}.
%systems. %This(e.g. ~\cite{NutanixPaper}).  Leading cloud platform companies
%such as Google, Amazon, Alibaba, Microsoft Azure  have built a converged
%compute and storage infrastructure and used a distributed file system such as
%Google file system~\cite{googlefs03,hdfs10} to glue a large number of
%commodity servers.
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the
%costs and performance limitations associated with network storage.
each physical machine runs a number of virtual machines (VMs)
%as  instances of a guest operating system 
and their virtual disks are stored as disk image files.
% typically using a local (possibly shared) file system.
Frequent snapshot backup of virtual machine images can
increase the service reliability by allowing VMs to restart from their latest
snapshot in the event of a server failure. Snapshots contain highly redundant content chunks and 
%  However, because the disk
%blocks that make up the VMs are often the same from snapshot to snapshot
%and are shared among VMs,  
deduplication of redundant 
content~\cite{venti02,bottleneck08} is necessary to substantially reduce the
storage demand.
